---
title: "Assignment 9"
author: "Isabeau Lewis"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading libraries
```{r}
library(doParallel)
library(parallel)
library(foreach)
```

# Running detectCores()
```{r}
Cores <- parallel::makeCluster(detectCores()) 
print(Cores)
```

According to the function, my system has 8 cores.

# Writing a for loop & tracking the time it takes to run
```{r}
current <- Sys.time() 

Samples <- vector(mode="numeric", length=4000)

for (i in 1:4000){
  Sample <- mean(rnorm(n=100000, mean=10, sd=3))
  Samples[i] <- Sample
}

after <- Sys.time()

Time <- after - current
print(Time)
```

# Predicting how much faster a multi-threaded program will run 
```{r}
prediction <- as.numeric(gsub("[[:alpha:]]", "", Time))
print(prediction)/detectCores()
```

I predict a multi-threaded program will run in about 6.7 seconds, 1/8 of the time it took to run the original code.

# Running in parallel

```{r}
# Finding the number of cores in my computer
Cores <- parallel::makeCluster(detectCores()) 

# Activating multi-threading based on the number of cores
doParallel::registerDoParallel(Cores) 
```

```{r}
current2 <- Sys.time() # to track runtime

# Running parallel R code
parallel <- foreach(i=1:4000, .combine=rbind) %dopar% {
  i = rnorm(n=100000, mean=10, sd=3)
}

after2 <- Sys.time() # to track runtime

Time2 <- after2 - current2
print(Time2)
```

```{r}
# De-activating multi-threading
parallel::stopCluster(Cores) 
```


# Summarizing results of theoretical vs. real run-time










